Palmer amaranth (\emph{Amaranthus palmeri}) adaptation to US Midwest agroecosystems

### 2021-09-17 Manuscript/table.tex
as

 & Weed control & glyphosate\textsuperscript{a} / \emph{S}-metolachor\textsuperscript{b} & saflufenacil + imazethapyr + pyroxasulfone\textsuperscript{c} &  &  & \\

@@

 & Hybrid & NK0142 3120-EZ1 & DKC60-67 &  &  & \\

 & Seeding rate & 88956 & 86487 &  &  & \\

 & Weed control & glyphosate / \emph{S}-metolachor & \emph{S}-metolachlor + trazine + mesotrione + bicyclopyrone\textsuperscript{d} &  &  & \\

 & Stage at 1\textsuperscript{st} cohort & V2-3 &  &  &  & \\

 & Stage at 2\textsuperscript{nd} cohort & V6-7 &  &  &  & \\

 & Planting day & April 30, 2018 / May 5, 2019 & May 10, 2018/19 &  &  & \\

\multirow{-7}{*}{\raggedright\arraybackslash } & Fertilization & N (46-0-0) at 157 kg ha\textsuperscript{-1} &  &  &  & \\

@@

 & Variety & DSR-1950 & AG21X8 &  &  & \\

 & Seeding rate & 296400 & 321237 &  &  & \\

 & Weed control & glyphosate / \emph{S}-metolachor & saflufenacil + imazethapyr + pyroxasulfone &  &  & \\

 & Stage at 1\textsuperscript{st} cohort & V1-2 &  &  &  & \\

 & Stage at 2\textsuperscript{nd} cohort & V5-6 &  &  &  & \\

\multirow{-6}{*}{\raggedright\arraybackslash } & Planting day & May 5, 2018 / May 10, 2009 & May 14, 2018/19 &  &  & \\

@@

 & Type & Plano-silt-loam & Crete Silt Loam &  &  & \\

 & Ratio (sand-clay-silt) & 10-64-26 & 17-58-25 &  &  & \\

 & pH & 6.6 & 6.5 &  &  & \\

\multirow{-4}{*}{\raggedright\arraybackslash } & Organic matter (\%) & 3.5 & 3 &  &  & \\
\bottomrule
\multicolumn{7}{l}{\rule{0pt}{1em}\textsuperscript{a} glyphoste, 840 g ae ha \textsuperscript{b} \emph{S}--metolachor, 1324 g ai ha; \textsuperscript{c} saflufenacil + imazethapyr + pyroxasulfone, 215 g ai ha; \textsuperscript{d} \emph{S}-metolachlor + trazine + mesotrione, + bicyclopyrone, 2409 g ai ha}\\
\end{tabular}}
\end{table}

>>>>

 & Weed control\textsuperscript{a} & \emph{S}-metolachor\textsuperscript{b} fb glyphosate\textsuperscript{c} /  & saflufenacil + imazethapyr + pyroxasulfone\textsuperscript{d} & glyphosate & glyphosate + \emph{S}-metolachor\textsuperscript{f} fb glyphosate\textsuperscript{g} & \\

@@

 & Hybrid & NK0142 3120-EZ1 & DKC60-67 & G03C84-5122-EZ1 & P1197AM & \\

 & Seeding rate & 88956 & 86487 & 79000 & 86485 & \\

 & Weed control & \emph{S}-metolachor fb glyphosate & \emph{S}-metolachlor + trazine + mesotrione + bicyclopyrone\textsuperscript{e} & glyphosate & glyphosate + \emph{S}-metolachor\textsuperscript{f} fb glyphosate\textsuperscript{g} & \\

 & Stage at 1\textsuperscript{st} cohort & V2-3 & V6-7 & V6-7 & V2-3 & \\

 & Stage at 2\textsuperscript{nd} cohort & V6-7 & V6-7 & V6-7 & V6-7 & \\

 & Planting day & April 30, 2018 / May 5, 2019 & May 10, 2018/19 & May 5, 2018 / May 14, 2019 & April 27, 2018 / May 3, 2019 & \\

\multirow{-7}{*}{\raggedright\arraybackslash } & Fertilization & N (46-0-0) at 157 kg ha\textsuperscript{-1} &  &  & N (46-0-0) at 336 kg ha\textsuperscript{-1} & \\

@@

 & Variety & DSR-1950 & AG21X8 & AG28X7 & 2018: 3017R2X; 2019 P31A22X & \\

 & Seeding rate & 296400 & 321237 & 220000 & 370650 & \\

 & Weed control & glyphosate / \emph{S}-metolachor & saflufenacil + imazethapyr + pyroxasulfone & glyphosate & glyphosate + \emph{S}-metolachor fb glyphosate & \\

 & Stage at 1\textsuperscript{st} cohort & V1-2 & V1-2 & V1-2 &  & \\

 & Stage at 2\textsuperscript{nd} cohort & V5-6 & V5-6 & V5-6 &  & \\

\multirow{-6}{*}{\raggedright\arraybackslash } & Planting day & May 5, 2018 / May 10, 2009 & May 14, 2018/19 & May 5, 2018 / May 14, 2019 & May 7, 2018 / May 17, 2019 & \\

@@

 & Type & Plano-silt-loam & Crete Silt Loam & 2018: Mace silt loam / 2019: Kuma silt loam & Crete silty clay loam & \\

 & pH & 6.6 & 6.5 & 2018: 6.1 / 2019: 5.1 & 5.2 & \\

\multirow{-4}{*}{\raggedright\arraybackslash } & Organic matter (\%) & 3.5 & 3 & 2018: 2 / 2019: 1.7 & 3.4 & \\
\bottomrule
\multicolumn{7}{l}{\rule{0pt}{1em}\textsuperscript{a}Hoe weeding; \textsuperscript{b}\emph{S}--metolachor, 1324 g ai ha\textsuperscript{-1}; \textsuperscript{c}glyphoste, 1262 g ae ha\textsuperscript{-1}; \textsuperscript{d}saflufenacil + imazethapyr + pyroxasulfone, 215 g ai ha\textsuperscript{-1}; \textsuperscript{e}\emph{S}-metolachlor + trazine + mesotrione, + bicyclopyrone, 2409 g ai ha\textsuperscript{-1}; \textsuperscript{f}\emph{S}--metolachor, 1070 g ai ha\textsuperscript{-1}; \textsuperscript{g}glyphoste, 870 g ae ha\textsuperscript{-1}} \\
\end{tabular}}
\end{table}
